Haploid Selection, Sex Ratio Bias, and Transitions Between sex-determination systems

### 2017-08-25 LaTeX/Turnover.tex
new supp figures

Overall, our models reveal that transitions between sex-determination systems, particularly transitions where the heterogametic sex changes, can be driven by loci in unexpected genomic locations that experience selection during diploid and/or haploid phases, which might be reflected by the lability with which sex-determination systems evolve. %and for the factors determining the phylogenetic pattern of sex-determination systems. 

@@

We find that sex-ratio biases caused by haploid selection can exert Fisherian sex-ratio selection upon novel sex-determiners but that their spread is also determined by selection on genetically-associated alleles. 
%Indeed, it is only when haploid-selected loci are tightly linked to the ancestral sex-determining region (and so sex-ratio biases are initially large) that we see an asymmetry between selection for XY to ZW transitions and ZW to XY transitions (e.g., because haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system).
Consequently, it is possible for selection on linked alleles to drive turnover between sex-determining systems despite causing transitory or even permanent increases in sex-ratio bias. 
Another significant feature of our model is that we consider selection loci that are under selection and also in very tight linkage with the ancestral sex-determining region.
Even in the absence of haploid selection, we show that transitions between male and female heterogamety can then evolve despite the fact that the neo-sex-determining locus is less closely linked to a locus under selection and therefore disrupts favourable ancestral associations between sex and the alleles selected in that sex.
%Such transitions are not favoured in models lacking tight linkage and/or haploid selection. 
%Secondly, we allow sex-specific haploid selection to occur on a locus in tight or loose linkage with the ancestral sex-determining region. 
%In addition, when linkage between the ancestral sex-determining locus and a locus under haploid selection is tight, sex ratio biases can be strong such that there is an asymmetry between invasion of ancestrally XY and ancestrally ZW systems because, e.g., haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system.

@@

If we categorise the $a$ allele as being ancestrally `male-beneficial' via the fact that it is fixed on the Y, then $\lambda_{mA}>1$ indicates that the neo-W spreads when found with the ancestrally `female-beneficial' allele. 
Broadly, this is possible because the ancestral X chromosome is not able to perfectly specialise on the `female-beneficial' allele due to the fact that X's are sometimes found in males. 
For example, when the $a$ allele is favoured in males, a polymorphism of $A$ and $a$ alleles can be maintained on the X despite directional selection in favour of the $A$ allele in females ($s^\female>0$, $0<h^\female<1$). 
Indeed, Figure \ref{fig:regionplots}A indicates that $\lambda_{mA}$ tends to be larger than one with sexually-antagonistic selection where the $a$ allele is strongly favoured in males ($w_{aa}$ much larger than $w_{Aa}$).
In this case, W-$A$ haplotypes will only create females with high fitness ($AA$ or $Aa$ genotypes) and therefore have higher fitness than ancestral females, which sometimes also produce $aa$ females. 
When only one neo-W haplotype can has a positive growth rate (see Figure \ref{fig:regionplots}), a neo-W can invade as long as equation \eqref{eq:lambdasGen} is satisfied, which may require that the recombination rate, $R$, is small enough.
Nevertheless, because we assume here that $r$ is small, these results indicate that a more loosely linked sex-determining region can spread.
Therefore, tightly sex-linked loci that experience sexually-antagonistic selection can drive heterogametic transitions in which the neo-SDR is less closely linked to the locus under selection (Figure \ref{fig:SexAntagTighter}). 
%Prediction (just an idea), considering sexually antagonistic selection alone, we should observe an excess of transitions between XY and ZW systems on the same chromosome because the tight linkage results indicate that there can be selection for heterogametic transitions but only when the neo-SDR is relatively closely linked (but not necessarily more closely linked).

@@

Both W-$A$ and W-$a$ haplotypes can spread, as is the case when $AA$ individuals have low fitness in females yet the $A$ is polymorphic or fixed on the X due to overdominance in males (Figure \ref{fig:regionplots}B and \ref{fig:regionplots}C).
Both neo-W-$A$ and neo-W-$a$ haplotypes then produce fewer unfit $AA$ females.
This is true for the neo-W-$A$ haplotype because it can pair with a $Y-a$ haplotype and still be female. 
Wherever both haplotypes have positive growth rates, invasion by a neo-W is expected regardless of its linkage with the selected locus (i.e., even unlinked neo-W alleles can invade, see Figures \ref{fig:positionOverdominance} and \ref{fig:temporalOverdominance} for examples).

@@

The green curves in Figure \ref{fig:SexRatioBad} demonstrate a case where transitions between male and female heterogametey occur even though the new sex-determining region is unlinked to a locus that experiences haploid and diploid selection. 
We use this example to discuss why heterogametic transitions can occur when $R=1/2$ and $r<1/2$, as in Table \ref{tab:specialcases}.
In Figure \ref{fig:SexRatioBad}B, an unlinked neo-W can spread because the zygotic sex ratio is ancestrally male biased. 
However, in Figure \ref{fig:SexRatioBad}A, an unlinked neo-Y spreads despite the fact that the ancestral zygotic sex ratio is even. 
In this case, the the male meiotic drive allele, $a$, is initially more common among ancestral-Z-bearing eggs than ancestral-W-bearing eggs because the Z is found in males more often than the W and $r<1/2$ (equation \ref{eq:freq_diffs}). 
%In this case, the ancestral male determining allele, Z, is initially associated with the male meiotic drive allele, $a$, because the Z is found in males more often than the W and $r<1/2$. 
Polymorphism at the \textbf{A} locus is maintained by counter-selection against the $a$ allele in diploids and therefore ancestral-ZZ males have generally low diploid fitness. 
A freely recombining neo-Y ($R=1/2$) is not directly favoured or dis-favoured by male meiotic drive because it is equally likely to be segregate with the $A$ or $a$ allele when found in a heterozygote.
The neo-Y spreads because it produces males with high diploid fitness through matings with ancestral-W-bearing female gametes, which are more likely to carry the $A$ allele. 
Thus, a key factor in explaining why heterogametic transitions can occur when $R>r$ is that that the neo-SDR determines sex in the diploid phase but then recombination occurs before any subsequent haploid selection.

@@

%Sex ratio biases caused by gametic competition or meiotic drive have been shown to exert Fisherian sex-ratio selection on various autosomal \citep{Stalker:1961th,Smith:1975ft,Frank:1989vl,Hough:2013uo,Ubeda:2015fx, Otto:2015va} and sex-linked \citep{Kozielska:2010vm} modifiers.
Sex-ratio biases caused by haploid selection can facilitate heterogametic transitions between sex-determining systems. 
For instance, alleles favoured by haploid selection in males often become associated with the Y, which leads to a male sex-ratio bias.
This male bias increases the potential for a neo-W to invade (Table \ref{tab:haplotype_growth}), which can equalize the sex-ratio \citep[e.g., see Figure \ref{fig:SexRatioBad}B, for related examples see][]{Kozielska:2010vm,Ubeda:2015fx}.
%We find that sex-ratio biases caused by haploid selection can also affect transitions between sex-determining systems (e.g., see $\zeta$ terms in Table \ref{tab:haplotype_growth}). 
%However, the neo-W may not equalize the sex-ratio (e.g., if the driving allele also drives in females or affects competition among eggs)
However, sex-ratio selection can be overwhelmed by additional selective effects (e.g., when a linked allele is beneficial for male diploids but detrimental for female diploids; Table \ref{tab:specialcases}), preventing the neo-W from invading. %and equalizing the sex ratio.
Indeed, transitions between sex-determining systems can even lead to stronger sex-ratio biases.
For example, where a neo-Y invades and is linked with a locus that experiences haploid selection in male gametes, the sex ratio evolves to become biased \citep[e.g., see Figure \ref{fig:SexRatioBad}A and step 1 in][]{Ubeda:2015fx}.
%For example, in an ancestral ZW system, haploid selection in males can allow a linked neo-Y to invade, despite the fact that it creates a male-biased sex ratio because the neo-Y becomes associated with the driven allele (Figure \ref{fig:SexRatioBad}A).
%\textcolor{blue}{and figure 1, where the end of one panel is the same as the beginning of another, however, this figure may change).}
%What we would like to stress is that sex-ratio selection alone cannot predict when new sex-determining systems can evolve.
Furthermore, with weak selection, we find that there is no difference in conditions allowing XY to ZW and ZW to XY transitions, indicating that sex chromosome transitions are not predominantly predicted by their effect on the sex-ratio (i.e., the sex-ratio bias created by male haploid selection facilitates the spread of a neo-W into an XY system the same way that male haploid selection drives the spread of a neo-Y into a ZW system with a 1:1 sex ratio). 
%An asymmetry can develop when sex-linkage is tight (e.g., Figure \ref{fig:Combination_Centimorgans} near -25cM and 25cM) but under most circumstances we do not predict asymmetry between XY to ZW and ZW to XY transitions despite the presence/absence of sex ratio selection. 
Thus, haploid selection can favour heterogametic transitions both via sex-ratio selection %\citep[as predicted by][]{Kozielska:2010vm} 
and via fitness effects of alleles that are associated with the neo-sex-determining allele, and these selection pressures are predicted to often be of roughly equal magnitude (unless linkage is tight). 
%\textcolor{red}{Maybe try to emphasise surprisingness in the paragraph more? e.g., how wrong you'd be if you assumed selection to equalise sex ratios, or it this implied?}
%\textcolor{blue}{nice, pretty subtle argument but I think that's a good job.}

@@

%COMPARATIVE PATTERNS 
We show that the spread of new sex determination systems can be driven by loci experiencing haploid selection. 
Because haploid selection can cause transitions that increase or decrease sex-linkage, haploid selection may lead to less stability, and greater potential for cycling, in sex-determination systems (e.g., the final state of the red line in Figure \ref{fig:SexRatioBad}A is the starting state in Figure \ref{fig:SexRatioBad}B). 
In particular, if haploid selection is strong but selective differences between male and female diploids are weak, we find that heterogametic transitions (XY to ZW or vice versa) are favoured more strongly than homogametic transitions (e.g., with $|D^\male - D^\female| << |\alpha_\Delta^\male - \alpha_\Delta^\female + t^\male - t^\female|$ we have $\lambda_{W',XY} > \lambda_{Y',XY}$; equations \ref{eq:lambda_neoW} and \ref{eq:freq_diffs}). 
Turnovers driven by haploid selection may help to explain the relative rarity of heteromorphic sex chromosomes in plants, which are thought to experience more selection during their multicellular haploid stage.
For example, among relatively few dioecious clades in which multiple species have well characterized sex chromosomes \citep{Ming:2011iy}, heterogametic transitions have been inferred in \textit{Silene} subsection \textit{Otites} \citep{Slancarova:2013dq} and in \textit{Salicaceae} \textcolor{red}{(Pucholt et al. 2015, 2017)}. 
%Potentially, successive heterogametic transitions between master regulators of sex-determination could be inferred from careful examination of the molecular pathways by which sex is determined. 
%Our predictions could also be examined using a suitable proxy for haploid selection, for example, \cite{Lenormand:2005vb} use the outcrossing rate in plants as a proxy for the strength of pollen competition. 
Furthermore, assuming that transitions from dioecy to hermaphroditism (equal parental investment in male and female gametes) are favoured in a similar manner to the ESD examined here (equal probability of zygotes developing as males or females), our results suggest that competition during the haploid stage could drive transitions between dioecy and hermaphroditism, which are frequent in plants \textcolor{red}{(Käfer et al., 2017, Sabath et al., 2017)}.  
%In animals, one might expect gametic competition to be stronger in species where sperm is required to live for a long time after spermatogenesis because transcripts shared during spermatogenesis may become depleted, revealing the haploid phenotype of the sperm \citep{Immler:2014im}.
%We would also expect that heterogametic transitions in sex determination would be more common in clades where there is meiotic drive.

@@

\begin{subequations}\label{Binvasion}
\begin{align}
\lambda_{mA}&= (2 \alpha^\male w_{A}^\male)^{-1}
\frac{w_{A}^\female }{w_{A}^\female}
\frac{\left[w_{A}^\male \alpha^\male w_{AA}^\female + 
w_{a}^\male (1-\alpha^\male) w_{Aa}^\female 2\alpha^\female\right]}
{ w_{A}^\female w_{AA}^\female } \\
\lambda_{ma}&= (2 \alpha^\male w_{A}^\male)^{-1} 
\frac{w_{a}^\female}{w_{A}^\female}
\frac{\left[ w_{A}^\male \alpha^\male w_{Aa}^\female2(1-\alpha^\female)+
w_{a}^\male (1-\alpha^\male) w_{aa}^\female \right]}
{ w_{A}^\female w_{AA}^\female } \\
\rho_{mA}&= (2 \alpha^\male w_{A}^\male)^{-1}
\frac{w_{A}^\female }{w_{A}^\female}
\frac{R w_{a}^\male (1-\alpha^\male) w_{Aa}^\female  \alpha^\female}
{ w_{AA}^\female } \\
\rho_{ma}&= (2 \alpha^\male w_{A}^\male)^{-1}
\frac{w_{a}^\female}{w_{A}^\female}
\frac{R w_{A}^\male \alpha^\male w_{Aa}^\female (1-\alpha^\female)}
{  w_{AA}^\female} 
\end{align}
\end{subequations}

@@

Similar equations can be derived for equilibrium (A) by subbing the equilibrium allele frequencies into Table \ref{tab:haplotype_growth}.

@@

\noindent  
where $\phi-\psi=w_{AA}^\female w_{Aa}^\male-w_{aa}^\female w_{aa}^\male$ and both $\phi$ and $\psi$ are positive when equilibrium (A) is stable. 
In contrast to equilibrium (B), a neo-W haplotype can spread under purely sexually-antagonistic selection  ($w_{AA}^\male>w_{Aa}^\male>w_{aa}^\male$ and $w_{AA}^\female>w_{Aa}^\female>w_{aa}^\female$).
The neo-W-$A$ can spread as long as it becomes associated with females that bear more $A$ alleles than observed at equilibrium (A). 
%In this case, the neo-W-$A$ haplotype can spread, despite producing a lot of $Aa$ daughters by obtaining the $a$ from Y-gametes, when $aa$ females, which the neo-W-$A$ never makes, are strongly selected against.
%This can be intuited from the fact that \eqref{eq:BeqWAspread} will be more easily met when $w_{Aa}^\female-w_{aa}^\female\approx w_{Aa}^\female$ and $w_{AA}^\female-w_{Aa}^\female\approx 0$, implying $w_{aa}^\female \approx 0$ and $w_{Aa}^\female\approx w_{AA}^\female$ (although this is complicated by the fact that $w_{aa}^\female$ and $w_{Aa}^\female$ affect $\phi$ and $\psi$ too, the intuition holds).

@@

@@

\textcolor{red}{
Check that we mention Sally's result that invasion cannot occur with sexually-antagonistic selection and $R=1/2$
}

\textcolor{red}{
We could also give versions of Figure \ref{fig:regionplots} where there is also haploid selection of various types. I suggest using $\alpha_{\Delta}^\Hermaphrodite=1/20$ and $t^\Hermaphrodite=1/10$. 
Haploid selection can favour $A$ or $a$, so this would involve 4x 6-panel figures. Started looking at this in RegionPlots.nb but haven't added gametic competition or labels for $\lambda$s. 
Try to integrate into the discussion of haploid selection?}

@@

\textcolor{red}{
Perhaps, for one set of parameters, we should plot the dynamics of all the different alleles. E.g., we could use the same parameters used in \ref{fig:SexRatioBad}. The main purpose would be to show what happens to the ancestral SDR during turnover. 
We could also show an example where XY and ZW sex determining systems are both polymorphic and stable.  
}

>>>>

Overall, our models reveal that transitions between sex-determination systems, particularly transitions where the heterogametic sex changes, can be driven by loci in previously unexpected genomic locations that experience selection during diploid and/or haploid phases.
These results might be reflected in the lability with which sex-determination systems evolve. %and for the factors determining the phylogenetic pattern of sex-determination systems. 

@@

We find that sex-ratio biases caused by haploid selection can exert Fisherian sex-ratio selection upon novel sex-determiners but that their spread is also determined by selection on genetically-associated alleles. 
%Indeed, it is only when haploid-selected loci are tightly linked to the ancestral sex-determining region (and so sex-ratio biases are initially large) that we see an asymmetry between selection for XY to ZW transitions and ZW to XY transitions (e.g., because haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system).
Consequently, it is possible for selection on linked alleles to drive turnover between sex-determining systems despite causing transitory or even permanent increases in sex-ratio bias. 
In addition to considering haploid selection, another novel development in our model is that we consider loci that are under diploid and/or haploid selection and also in very tight linkage with the ancestral sex-determining region.
Even in the absence of haploid selection, we show that transitions between male and female heterogamety can then evolve despite the fact that the neo-sex-determining locus is less closely linked to a locus under selection and therefore disrupts favourable ancestral associations between sex and the alleles selected in that sex.
%Such transitions are not favoured in models lacking tight linkage and/or haploid selection. 
%Secondly, we allow sex-specific haploid selection to occur on a locus in tight or loose linkage with the ancestral sex-determining region. 
%In addition, when linkage between the ancestral sex-determining locus and a locus under haploid selection is tight, sex ratio biases can be strong such that there is an asymmetry between invasion of ancestrally XY and ancestrally ZW systems because, e.g., haploid selection in males only causes biased zygotic sex ratios in an ancestrally XY system.

@@

If we categorise the $a$ allele as being ancestrally `male-beneficial' via the fact that it is fixed on the Y, then $\lambda_{mA}>1$ indicates that the neo-W spreads when found with the ancestrally `female-beneficial' allele. 
Broadly, this is possible because the ancestral X chromosome is not able to perfectly specialise on the `female-beneficial' allele due to the fact that X's are sometimes found in males. 
For example, when the $a$ allele is favoured in males, a polymorphism of $A$ and $a$ alleles can be maintained on the X despite directional selection in favour of the $A$ allele in females ($s^\female>0$, $0<h^\female<1$). 
Figure \ref{fig:regionplots}A indicates that $\lambda_{mA}$ tends to be larger than one with sexually-antagonistic selection where the $a$ allele is strongly favoured in males ($w_{aa}$ much larger than $w_{Aa}$). 
In this case the $a$ allele is at high frequency among XX females is high due to selection upon the X in males. 
By contrast, W-$A$ haplotypes will only create females with high fitness ($AA$ or $Aa$ genotypes) and can therefore have higher fitness than ancestral females. 
When only one neo-W haplotype can has a positive growth rate (see Figure \ref{fig:regionplots}), a neo-W can invade as long as equation \eqref{eq:lambdasGen} is satisfied, which may require that the recombination rate, $R$, is small enough.
Nevertheless, because we assume here that $r$ is small, these results indicate that a more loosely linked sex-determining region can spread.
Therefore, tightly sex-linked loci that experience sexually-antagonistic selection can drive heterogametic transitions in which the neo-SDR is less closely linked to the locus under selection (Figure \ref{fig:SexAntagTighter}). 
%Prediction (just an idea), considering sexually antagonistic selection alone, we should observe an excess of transitions between XY and ZW systems on the same chromosome because the tight linkage results indicate that there can be selection for heterogametic transitions but only when the neo-SDR is relatively closely linked (but not necessarily more closely linked).

@@

In some cases, both W-$A$ and W-$a$ haplotypes can spread, e.g., when $AA$ individuals have low fitness in females yet the $A$ is polymorphic or fixed on the X due to overdominance in males (Figure \ref{fig:regionplots}B and \ref{fig:regionplots}C).
Both neo-W-$A$ and neo-W-$a$ haplotypes then produce fewer unfit $AA$ females.
This is true for the neo-W-$A$ haplotype because it can pair with a $Y-a$ haplotype and still be female. 
Wherever both haplotypes have positive growth rates, invasion by a neo-W is expected regardless of its linkage with the selected locus (i.e., even unlinked neo-W alleles can invade, see Figures \ref{fig:positionOverdominance} and \ref{fig:temporalOverdominance} for examples).

@@

The green curves in Figure \ref{fig:SexRatioBad} demonstrate a case where transitions between male and female heterogametey occur even though the new sex-determining region is unlinked to a locus that experiences haploid and diploid selection. 
We use these green curves to discuss why heterogametic transitions can occur when $R=1/2$ and $r<1/2$, as in Table \ref{tab:specialcases}.
In Figure \ref{fig:SexRatioBad}B, an unlinked neo-W can spread because the zygotic sex ratio is ancestrally male biased. 
However, in Figure \ref{fig:SexRatioBad}A, an unlinked neo-Y spreads despite the fact that the ancestral zygotic sex ratio is even. 
In this case, the the male meiotic drive allele, $a$, is initially more common among ancestral-Z-bearing eggs than ancestral-W-bearing eggs because the Z is found in males more often than the W and $r<1/2$ (equation \ref{eq:freq_diffs}). 
%In this case, the ancestral male determining allele, Z, is initially associated with the male meiotic drive allele, $a$, because the Z is found in males more often than the W and $r<1/2$. 
Polymorphism at the \textbf{A} locus is maintained by counter-selection against the $a$ allele in diploids and therefore ancestral-ZZ males have generally low diploid fitness. 
A freely recombining neo-Y ($R=1/2$) is not directly favoured or dis-favoured by male meiotic drive because it is equally likely to be segregate with the $A$ or $a$ allele when found in a heterozygote.
The neo-Y spreads because it produces males with high diploid fitness through matings with ancestral-W-bearing female gametes, which are more likely to carry the $A$ allele. 
Thus, a key factor in explaining why heterogametic transitions can occur when $R>r$ is that that the neo-SDR determines sex in the diploid phase but recombination occurs before any subsequent haploid selection.

@@

%Sex ratio biases caused by gametic competition or meiotic drive have been shown to exert Fisherian sex-ratio selection on various autosomal \citep{Stalker:1961th,Smith:1975ft,Frank:1989vl,Hough:2013uo,Ubeda:2015fx, Otto:2015va} and sex-linked \citep{Kozielska:2010vm} modifiers.
Sex-ratio biases caused by haploid selection can facilitate heterogametic transitions between sex-determining systems. 
For instance, alleles favoured by haploid selection in males often become associated with the Y, which leads to a male-biased zygotic sex-ratio.
This male bias increases the potential for a neo-W to invade (Table \ref{tab:haplotype_growth}), which can equalize the sex-ratio \citep[e.g., see Figure \ref{fig:SexRatioBad}B, for related examples see][]{Kozielska:2010vm,Ubeda:2015fx}.
%We find that sex-ratio biases caused by haploid selection can also affect transitions between sex-determining systems (e.g., see $\zeta$ terms in Table \ref{tab:haplotype_growth}). 
%However, the neo-W may not equalize the sex-ratio (e.g., if the driving allele also drives in females or affects competition among eggs)
However, sex-ratio selection can be overwhelmed by additional selective effects (e.g., when a linked allele is beneficial for male diploids but detrimental for female diploids; Table \ref{tab:specialcases}), preventing the neo-W from invading. %and equalizing the sex ratio.
Indeed, transitions between sex-determining systems can even lead to stronger sex-ratio biases.
For example, where a neo-Y invades and is linked with a locus that experiences haploid selection in male gametes, the sex ratio evolves to become biased \citep[e.g., see Figure \ref{fig:SexRatioBad}A and step 1 in][]{Ubeda:2015fx}.
%For example, in an ancestral ZW system, haploid selection in males can allow a linked neo-Y to invade, despite the fact that it creates a male-biased sex ratio because the neo-Y becomes associated with the driven allele (Figure \ref{fig:SexRatioBad}A).
%\textcolor{blue}{and figure 1, where the end of one panel is the same as the beginning of another, however, this figure may change).}
%What we would like to stress is that sex-ratio selection alone cannot predict when new sex-determining systems can evolve.
Furthermore, with weak selection, we find that there is no difference in conditions allowing XY to ZW and ZW to XY transitions, indicating that sex chromosome transitions are not predominantly predicted by their effect on the sex-ratio (i.e., the sex-ratio bias created by male haploid selection facilitates the spread of a neo-W into an XY system the same way that male haploid selection drives the spread of a neo-Y into a ZW system with a 1:1 sex ratio). 
%An asymmetry can develop when sex-linkage is tight (e.g., Figure \ref{fig:Combination_Centimorgans} near -25cM and 25cM) but under most circumstances we do not predict asymmetry between XY to ZW and ZW to XY transitions despite the presence/absence of sex ratio selection. 
Thus, haploid selection can favour heterogametic transitions both via sex-ratio selection %\citep[as predicted by][]{Kozielska:2010vm} 
and via fitness effects of alleles that are associated with the neo-sex-determining allele, and these selection pressures are predicted to often be of roughly equal magnitude (unless linkage is tight). 
%\textcolor{red}{Maybe try to emphasise surprisingness in the paragraph more? e.g., how wrong you'd be if you assumed selection to equalise sex ratios, or it this implied?}
%\textcolor{blue}{nice, pretty subtle argument but I think that's a good job.}

@@

%COMPARATIVE PATTERNS 
We have shown that the spread of new sex determination systems can be driven by loci experiencing haploid selection. 
Because haploid selection can cause transitions that increase or decrease sex-linkage, haploid selection may lead to less stability, and greater potential for cycling, in sex-determination systems (e.g., the final state of the red line in Figure \ref{fig:SexRatioBad}A is the starting state in Figure \ref{fig:SexRatioBad}B). 
In particular, if haploid selection is strong but selective differences between male and female diploids are weak, we find that heterogametic transitions (XY to ZW or vice versa) are favoured more strongly than homogametic transitions (e.g., with $|D^\male - D^\female| << |\alpha_\Delta^\male - \alpha_\Delta^\female + t^\male - t^\female|$ we have $\lambda_{W',XY} > \lambda_{Y',XY}$; equations \ref{eq:lambda_neoW} and \ref{eq:freq_diffs}). 
Turnovers driven by haploid selection may help to explain the relative rarity of heteromorphic sex chromosomes in plants, which are thought to experience more selection during their multicellular haploid stage.
For example, among relatively few dioecious clades in which multiple species have well characterized sex chromosomes \citep{Ming:2011iy}, heterogametic transitions have been inferred in \textit{Silene} subsection \textit{Otites} \citep{Slancarova:2013dq} and in \textit{Salicaceae} \textcolor{red}{(Pucholt et al. 2015, 2017)}. 
%Potentially, successive heterogametic transitions between master regulators of sex-determination could be inferred from careful examination of the molecular pathways by which sex is determined. 
%Our predictions could also be examined using a suitable proxy for haploid selection, for example, \cite{Lenormand:2005vb} use the outcrossing rate in plants as a proxy for the strength of pollen competition. 
Furthermore, assuming that transitions from dioecy to hermaphroditism (equal parental investment in male and female gametes) are favoured in a similar manner to the ESD examined here (equal probability of zygotes developing as males or females), our results suggest that competition during the haploid stage could drive transitions between dioecy and hermaphroditism, which are frequent in plants \textcolor{red}{(Käfer et al., 2017, Sabath et al., 2017)}.  
%In animals, one might expect gametic competition to be stronger in species where sperm is required to live for a long time after spermatogenesis because transcripts shared during spermatogenesis may become depleted, revealing the haploid phenotype of the sperm \citep{Immler:2014im}.
%We would also expect that heterogametic transitions in sex determination would be more common in clades where there is meiotic drive.

@@

\begin{subequations}\label{Binvasion}
\begin{align}
\lambda_{mA}&= (2 \alpha^\male w_{A}^\male)^{-1}
\frac{w_{A}^\female }{w_{A}^\female}
\frac{\left[w_{A}^\male \alpha^\male w_{AA}^\female + 
w_{a}^\male (1-\alpha^\male) w_{Aa}^\female 2\alpha^\female\right]}
{ w_{AA}^\female } \\
\lambda_{ma}&= (2 \alpha^\male w_{A}^\male)^{-1} 
\frac{w_{a}^\female}{w_{A}^\female}
\frac{\left[ w_{A}^\male \alpha^\male w_{Aa}^\female2(1-\alpha^\female)+
w_{a}^\male (1-\alpha^\male) w_{aa}^\female \right]}
{ w_{AA}^\female } \\
\rho_{mA}&= (2 \alpha^\male w_{A}^\male)^{-1}
\frac{w_{A}^\female }{w_{A}^\female}
\frac{R w_{a}^\male (1-\alpha^\male) w_{Aa}^\female  \alpha^\female}
{ w_{AA}^\female } \\
\rho_{ma}&= (2 \alpha^\male w_{A}^\male)^{-1}
\frac{w_{a}^\female}{w_{A}^\female}
\frac{R w_{A}^\male \alpha^\male w_{Aa}^\female (1-\alpha^\female)}
{  w_{AA}^\female} 
\end{align}
\end{subequations}

@@

Similar equations can be derived for equilibrium (A) by substituting the equilibrium allele frequencies into Table \ref{tab:haplotype_growth}.

@@

\noindent  
where $\phi-\psi=w_{AA}^\female w_{Aa}^\male-w_{aa}^\female w_{aa}^\male$ and both $\phi$ and $\psi$ are positive when equilibrium (A) is stable. 
In contrast to equilibrium (B), a neo-W haplotype can spread under purely sexually-antagonistic selection  ($w_{AA}^\male<w_{Aa}^\male<w_{aa}^\male$ and $w_{AA}^\female>w_{Aa}^\female>w_{aa}^\female$).
The neo-W-$A$ can spread as long as it becomes associated with females that bear more $A$ alleles than observed at equilibrium (A). 
%In this case, the neo-W-$A$ haplotype can spread, despite producing a lot of $Aa$ daughters by obtaining the $a$ from Y-gametes, when $aa$ females, which the neo-W-$A$ never makes, are strongly selected against.
%This can be intuited from the fact that \eqref{eq:BeqWAspread} will be more easily met when $w_{Aa}^\female-w_{aa}^\female\approx w_{Aa}^\female$ and $w_{AA}^\female-w_{Aa}^\female\approx 0$, implying $w_{aa}^\female \approx 0$ and $w_{Aa}^\female\approx w_{AA}^\female$ (although this is complicated by the fact that $w_{aa}^\female$ and $w_{Aa}^\female$ affect $\phi$ and $\psi$ too, the intuition holds).

@@

\begin{figure}[!h]
\centering
\centerline{\includegraphics[width=1.5\linewidth]{PositionPlot_SexAntagTighter_MaleDrive_Mike}}
\caption{
When there is haploid selection and sexually-antagonistic selection, a neo-W may invade for any $R$.
\textcolor{red}{
Check that we mention Sally's result that invasion cannot occur with sexually-antagonistic selection and $R=1/2$ (currently only in legend for figure \ref{fig:SexAntagTighter}) 
Add asterisk to Figure \ref{fig:regionMaleDrive}B to show parameters used in this plot. 
}
$w_{aa}^\female=1.05$, $w_{Aa}^\Hermaphrodite=1$, $w_{AA}^\female=0.85$, $w_{aa}^\male=0.85$, $w_{AA}^\female=1.05$, $\alpha_{\Delta}^\male=-0.08$.
}
\label{fig:SexAntagTighterMaleDrive}
\end{figure}

\newpage
\begin{figure}[!h]
\centering
\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_MaleGS_Mike}}
\caption{
ABC, $w_{a}^\male=1.16$, $w_{A}^\male=1$.
DEF, $w_{a}^\male=1$, $w_{A}^\male=1.16$. 
\textcolor{red}{I thought that re-running this with $w_{a}^\male=1.16$, $w_{A}^\male=0.84$ and $w_{a}^\male=0.84$, $w_{A}^\male=1.16$ will mean that it matches exactly with the meiotic drive example. Checking for panel A, the result was qualitatively similar (e.g., region where both $\lambda$'s are greater than one in panel A, as you might expect from equation \eqref{Binvasion}, however the region where a polymorphism is stable is also altered so they don't exactly match. }
}
\label{fig:regionMaleGS}
\end{figure}

\begin{figure}[!h]
\centering
\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_MaleDrive_Mike}}
\caption{
ABC, $\alpha_{\Delta}^\male=-0.08$
DEF, $\alpha_{\Delta}^\male=0.08$. \textcolor{red}{Panel F mislabelled, should have $\lambda_{Wa}>1$ \& $\lambda_{WA}<1$ as the upper label that has the line.}
}
\label{fig:regionMaleDrive}
\end{figure}

\begin{figure}[!h]
\centering
\centerline{\includegraphics[width=\linewidth]{Region_Plot_combined_FemaleDrive_Mike}}
\caption{
ABC, $\alpha_{\Delta}^\female=-0.08$
DEF, $\alpha_{\Delta}^\female=0.08$. $\lambda$s are increased for the haplotype that is favoured by female haploid selection, the stability conditions are also affected. 
}
\label{fig:regionFemaleDrive}
\end{figure}

@@

@@

\textcolor{red}{
We could also give versions of Figure \ref{fig:regionplots} where there is also haploid selection of various types.
Haploid selection can favour $A$ or $a$, so this would involve 4x 6-panel figures. Started looking at this in Figure \ref{fig:regionMaleGS} and Figure \ref{fig:regionMaleDrive}, add female haploid selection. 
Try to integrate into the discussion of haploid selection? e.g., male haploid selection ones generally show effect of sex ratio, increasing both lambdas when female biased (top rows).}

\textcolor{red}{
Perhaps, for one set of parameters, we should plot the dynamics of all the different alleles. E.g., we could use the same parameters used in \ref{fig:SexRatioBad}. The main purpose would be to show what happens to the ancestral SDR during turnover. 
We could also show an example where XY and ZW sex determining systems are both polymorphic and stable (e.g., using one of the curves in Figure \ref{fig:temporalOverdominance} and the green curve in Figure \ref{fig:SexAntagTighterMaleDrive}). 
I think there are also examples with looser sex linkage and pollen competition that lead to a mixed sex-determination system. We should probably have a short section in the appendix discussing this. 
}
